\bf Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-08-26 paper.qmd
Updated Figure 17 caption

error_plot_mnist <- error_df |>
  ggplot(aes(x = PaCMAP1,
             y = PaCMAP2, 
             color = type, 
             group = ID)) +
  geom_point(alpha=0.5, 
             size = 0.1) #+
  #interior_annotation("b", sc_ltr_pos_mnist)
```

@@

```{r}
#| echo: false
#| fig-cap: "$10\\text{-}D$ model error in $2\\text{-}D$. The $2\\text{-}D$ model shows a non-linear continuous structure. Most low $10\\text{-}D$ model errors are distributed along the lower edge of the $2\\text{-}D$ structure, while most large $10\\text{-}D$ model errors are concentrated along the upper edge."
#| label: fig-model-mnist
#| fig-pos: H
#| out-height: 22%

error_plot_mnist + 
  plot_layout(guides='collect') &
  theme(legend.position='bottom')
```

There are certain data points that exhibit high error rates due to their deviation from the usual $10\text{-}D$ data structure, which makes them anomalies (@fig-model-mnist). These anomalies can be classified into two types: those that are anomalies within the non-linear structure and those that lie outside of it. The images associated with high model error points within the non-linear structure display different patterns of the digit 1, as shown in @fig-mnist1-within. However, when comparing these images to the ones found outside of the non-linear structure, it becomes evident that the latter display different patterns of the digit 1 (@fig-mnist1-out).

>>>>

error_plot_mnist <- error_df |>
  ggplot(aes(x = PaCMAP1,
             y = PaCMAP2, 
             color = type, 
             group = ID)) +
  geom_point(alpha=0.5, 
             size = 0.1) +
  scale_colour_brewer(
    type = "qual",
    palette = 2
  ) + 
  theme(
      legend.position = "bottom",
      legend.text = element_text(size = 10),          # Increase legend text size
      legend.key.size = unit(1, "lines")              # Increase size of legend keys
  ) +
  guides(
      color = guide_legend(
          override.aes = list(size = 2.5, alpha = 1)      # Increase point size and opacity in legend
      )
  )
```

@@

```{r}
#| echo: false
#| fig-cap: "$10\\text{-}D$ model error in PaCMAP layout of MNIST digit 1 dataset in $2\\text{-}D$. Most low $10\\text{-}D$ model errors are distributed along the lower edge of the $2\\text{-}D$ structure, while most large $10\\text{-}D$ model errors are concentrated along the upper edge (a). There are certain data points that exhibit high error rates due to their deviation from the usual $10\\text{-}D$ data structure, which makes them anomalies. These anomalies can be classified into two types: those that are anomalies within the non-linear structure and those that lie outside of it. The images associated with high model error points within the non-linear structure display different patterns of the digit 1 (b). However, when comparing these images to the ones found outside of the non-linear structure, it becomes evident that the latter display different patterns of the digit 1 (c). "
#| label: fig-model-mnist
#| fig-pos: H

error_plot_mnist 
```

<!-- There are certain data points that exhibit high error rates due to their deviation from the usual $10\text{-}D$ data structure, which makes them anomalies (@fig-model-mnist). These anomalies can be classified into two types: those that are anomalies within the non-linear structure and those that lie outside of it. The images associated with high model error points within the non-linear structure display different patterns of the digit 1, as shown in @fig-mnist1-within. However, when comparing these images to the ones found outside of the non-linear structure, it becomes evident that the latter display different patterns of the digit 1 (@fig-mnist1-out).  -->

### 2024-08-26 paper.tex
Updated Figure 17 caption

\includegraphics[width=1\textwidth,height=0.22\textheight]{paper_files/figure-pdf/fig-model-mnist-1.pdf}

@@

\caption{\label{fig-model-mnist}\(10\text{-}D\) model error in
\(2\text{-}D\). The \(2\text{-}D\) model shows a non-linear continuous
structure. Most low \(10\text{-}D\) model errors are distributed along
the lower edge of the \(2\text{-}D\) structure, while most large
\(10\text{-}D\) model errors are concentrated along the upper edge.}

@@

There are certain data points that exhibit high error rates due to their
deviation from the usual \(10\text{-}D\) data structure, which makes
them anomalies (Figure~\ref{fig-model-mnist}). These anomalies can be
classified into two types: those that are anomalies within the
non-linear structure and those that lie outside of it. The images
associated with high model error points within the non-linear structure
display different patterns of the digit 1, as shown in
Figure~\ref{fig-mnist1-within}. However, when comparing these images to
the ones found outside of the non-linear structure, it becomes evident
that the latter display different patterns of the digit 1
(Figure~\ref{fig-mnist1-out}).

>>>>

\includegraphics[width=1\textwidth,height=\textheight]{paper_files/figure-pdf/fig-model-mnist-1.pdf}

@@

\caption{\label{fig-model-mnist}\(10\text{-}D\) model error in PaCMAP
layout of MNIST digit 1 dataset in \(2\text{-}D\). Most low
\(10\text{-}D\) model errors are distributed along the lower edge of the
\(2\text{-}D\) structure, while most large \(10\text{-}D\) model errors
are concentrated along the upper edge (a). There are certain data points
that exhibit high error rates due to their deviation from the usual
\(10\text{-}D\) data structure, which makes them anomalies. These
anomalies can be classified into two types: those that are anomalies
within the non-linear structure and those that lie outside of it. The
images associated with high model error points within the non-linear
structure display different patterns of the digit 1 (b). However, when
comparing these images to the ones found outside of the non-linear
structure, it becomes evident that the latter display different patterns
of the digit 1 (c).}

@@
